The value of intermediation

### 2022-09-13 src/presentation/presentation.qmd
Add two-sided extension

@@

@@

::: {#prp-multiple-platforms .fragment}
## Multiple platforms
The limit of the Shapley-value (as $n \to \infty$) of each player of type $P$ is
$$
\begin{aligned}
   \varphi_{P_i}^{\infty, m} = \int_0^1 (1-t) ^ {m-1} f(t) \mathrm{d}t .
\end{aligned}
$$
:::

@@

>>>>

::: {.notes}
 - Relevance to competition policy
 - However: today's presentation is mostly theory but if I have time I'll say a few words about applications
:::

@@

::: {#prp-multiple-platforms .fragment}
## Multiple platforms
The limit of the Shapley-value (as $n \to \infty$) of each player of type $P$ is
$$
\varphi_{P_i}^{\infty, m} = \int_0^1 (1-t) ^ {m-1} f(t) \mathrm{d}t .
$$
:::

@@

@@

## Two-sided bargaining

::: {.column width="45%"}
Imagine that there are two fringe types ($A_i$ and $B_i$)
:::

::: {.column .fragment width="45%"}
$$
    v(S) = \begin{cases}
        0 \; \text{ if } P \notin S \\
        f\left(\frac{\#_A(S)}{n}, \frac{\#_B(S)}{n}\right).
    \end{cases}
$$
:::

::: {#prp-multiple-platforms .fragment}
## Two-sided bargaining
Let $f(a, b)$ continuous on $[0, 1] \times [0, 1]$. Then
$$
f(1, 1) = \underbrace{\int_0^1 f(t, t) \mathrm{d}t}_{\varphi_P^\infty(f)} + \underbrace{\int_0^1 t \frac{\partial f(t, t)}{\partial a} \mathrm{d}t}_{\varphi_A^\infty(f)} + \underbrace{\int_0^1 t \frac{\partial f(t, t)}{\partial b} \mathrm{d}t}_{\varphi_B^\infty(f)}
$$
:::

::: {.notes}
 - The other side (e.g. consumers) also participates in the bargaining process
 - Values are weighted marginal contributions
 - $P$ does not have to be in the "middle" of the transactions
:::
